---
title: "RPMI_PR_20200728"
author: "Liz Hughes"
date: "13/01/2022"
output:
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

#Plate reader assay#2.

##Test WT H99 and GAt 201 deletion mutants 003(Madhani) and 004(Bahn)in RPMI only.
##7 Bioreps, 3 Techreps each. (NB only 2 Techreps for Biorep 7)
##Grow 5ml culture from colony (1 colony = 1 Biorep)in YPD, 30C, 250 rpm ON.
##Seed at )D 600nm = 0.2 , 200 ul per well.
##Run for 3 days.
```{r load_packages}
library("reshape2")
library(dplyr)
library(ggplot2)
library(tidyverse)
library(markdown)
library(cowplot)
```



# Read in transposed data as csv file

```{r csv_file}
rawdata <- read.csv("../PR_Data_Gat201/20200728_EH_PR2_RPMI_WT_Gat201TRSP.csv")

```

# Change time in seconds to time in hours

```{r mutate_time}
 rawdata_hrs<-mutate(rawdata, Time = Time/86400)

```

# Tidy the data using the melt function from reshape2

```{r reshape}
reshaped <- melt(rawdata_hrs, id=c("Time", "Temp"), 
                              variable.name="Well",
                              value.name="OD595")

summary(reshaped)
```

# Read in the Plate map data from csv file

```{r Load_platemap}

platemap <- read.csv("../PR_Data_Gat201/20200728-PR2_SetupCSV.csv")
head(platemap, n=10)


```

# Combine the reshaped data with the plate map, pairing them by Well

```{r join}
annotated <- inner_join(reshaped, platemap, by="Well")
 
```

# How stable are ODs of blank wells, to use for normalisation?

```{r plot_blank_ODs}
ggplot(data=filter(annotated,Strain==""), 
       aes(x=Time, y=OD595, color=Strain, group = Well)) + 
       geom_line() + 
       facet_grid(Medium ~ .) +
       labs(x="Time (hrs)", y="Absorbance at 595 nm")
```
These are very stable, except H2. Remove from normalisation.

## Calculate median OD for blank wells for each growth medium
Remove well H2
```{r calc_blank_medians}
blank_OD_summary <- annotated %>%
  filter(Strain=="") %>%
  filter(Well != "H2") %>%
  # filter out columns 1 and 12 as well?
  group_by(Medium) %>%
  summarise(OD_median=median(OD595),
            OD_mean=mean(OD595),
            OD_max=max(OD595),
            OD_min=min(OD595))
print(blank_OD_summary)
```

# Subtract blank OD to make corrected OD and Plot OD_corrected v Time (hrs)

```{r subtract_blank_OD}
normalisedOD <- annotated %>%
  left_join(blank_OD_summary, by="Medium") %>%
  mutate(OD_corrected = OD595 - OD_median)

```

## Plot OD all 

```{r plot_all}
ggplot(data=normalisedOD %>%
                      filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain, group = Well)) + 
       geom_line() + 
       scale_y_continuous(limits=c(0,0.1),expand=c(0,0))+
       
  
       labs(x = "Time(Hrs)",
            y = "Absorbance (595nm)") +
       theme(text = element_text(size = 20))+
       theme_bw()+
       scale_color_brewer(palette="Set1")
```


## Plot OD all stat_summary(geom -"line")

```{r plot_all_stat_summary}
ggplot(data=normalisedOD %>%
                     filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 1) +
       scale_y_continuous(limits=c(0,0.1),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
  
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "Cell Culture Media") +
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 25)) +
  theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 30))+
       theme(legend.title = element_text(size = 25))+
  theme(panel.grid.minor = element_blank())+
       scale_color_brewer(palette="Set1")
```


```{r}
ggsave("~/GitHub/PR_Data_Gat201/RMPI_PR_Gat201.png",width = 7,height=5)
```



